---
title: "EQ5D comparisons"
author: "PHOSP-COVID collaborative"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  word_document:
    reference_docx: template.docx 
---

```{r setup, include=FALSE}
if (knitr::is_html_output()){
  knitr::opts_chunk$set(echo = TRUE,
                        warning = FALSE,
                        message = FALSE)
} else {
  knitr::opts_chunk$set(echo = FALSE,
                        warning = FALSE,
                        message = FALSE)
}

library(finalfit)
library(knitr)
library(tidyverse)
library(rmarkdown)

summary_factorlist <- purrr::partial(finalfit::summary_factorlist, na_to_prop = FALSE)

mykable = function(x, align = c("l", "l", "r", "r", "r", "r", "r", "r", "r", "r", "r"), ...){
  knitr::kable(x,  
               booktabs = TRUE, 
               linesep = "", ...) 
}
```

```{r}
# Made in 00_analysis.Rmd
load("full_image_090621.Rdata")
```

## When was pre-COVID EQ5D administered?

```{r}
# EQ5D variables

# When waspre-completed?
phosp %>% 
  select(study_id, redcap_event_name, eq5d5l_q1_pre) %>% 
  drop_na() %>% 
  select(-eq5d5l_q1_pre) %>% 
  arrange(redcap_event_name) %>% 
  group_by(study_id) %>% 
  summarise(event = paste(redcap_event_name, collapse = "_")) %>% 
  ungroup() %>% 
  count(event) %>% 
  arrange(-n) %>% 
  mykable()
```

## How did pre-COVID EQ5D vary by visit?

```{r fig.height=8, fig.width=12}
phosp %>% 
  select(study_id, redcap_event_name, matches("eq5d5l_[q12345]*_pre_numeric")) %>% 
  mutate(redcap_event_name = fct_relabel(redcap_event_name, str_trunc, width = 8, ellipsis = "")) %>% 
  pivot_longer(matches("eq5d5l_[q12345]*_pre_numeric")) %>% 
  drop_na() %>% 
  ggplot_lancet(aes(x = redcap_event_name, y = value, group = study_id)) + 
  geom_line(position=position_jitter(w=0.2, h=0.2), alpha = 0.2) + 
  facet_wrap(.~ name)
```

## How different were results?

Of those that had it measured on more than one occasion, how did it compare? 

* \>0 worse
* \<0 better

```{r eval=FALSE, include=FALSE}
phosp %>% 
  filter(is.na(redcap_repeat_instance)) %>% 
  select(study_id, redcap_event_name, matches("eq5d5l_[q12345]*_pre_numeric")) %>% 
  drop_na() %>% 
  group_by(study_id) %>% 
  mutate(across(matches("eq5d5l_[q12345]*_pre_numeric"), ~ .x - lag(.x))) %>% 
  drop_na() %>% 
  ungroup() %>% 
  pivot_longer(matches("eq5d5l_[q12345]*_pre_numeric"), values_to = "Difference in value later minus earlier") %>% 
  count(name, `Difference in value later minus earlier`) %>%
  mutate(name = finalfit:::rm_duplicates(name)) %>% 
  mykable(align = c("l", "r", "r"))
```

```{r}
phosp %>% 
  filter(is.na(redcap_repeat_instance)) %>% 
  select(study_id, redcap_event_name, matches("eq5d5l_[q12345]*_pre_numeric")) %>% 
  drop_na() %>% 
  group_by(study_id) %>% 
  mutate(across(matches("eq5d5l_[q12345]*_pre_numeric"), ~ .x - lag(.x))) %>% 
  drop_na() %>% 
  ungroup() %>% 
  pivot_longer(matches("eq5d5l_[q12345]*_pre_numeric"), values_to = "Difference in value later minus earlier") %>% 
  count(name, `Difference in value later minus earlier`) %>%
  ggplot_lancet(aes(x = factor(`Difference in value later minus earlier`), y = n)) + 
  geom_col() + 
  facet_wrap(. ~ name) + 
  xlab("Difference in value later minus earlier (greater is worse)")
```

## When was post-COVID EQ5D administered?

```{r}
# EQ5D variables

# When waspre-completed?
phosp %>% 
  select(study_id, redcap_event_name, eq5d5l_q1) %>% 
  drop_na() %>% 
  select(-eq5d5l_q1) %>% 
  arrange(redcap_event_name) %>% 
  group_by(study_id) %>% 
  summarise(event = paste(redcap_event_name, collapse = "_")) %>% 
  ungroup() %>% 
  count(event) %>% 
  arrange(-n) %>% 
  mykable()
```

## How did post-COVID EQ5D vary by visit?

```{r fig.height=8, fig.width=12}
phosp %>% 
  select(study_id, redcap_event_name, matches("eq5d5l_[q12345]*_numeric")) %>% 
  mutate(redcap_event_name = fct_relabel(redcap_event_name, str_trunc, width = 8, ellipsis = "")) %>% 
  pivot_longer(matches("eq5d5l_[q12345]*_numeric")) %>% 
  drop_na() %>% 
  ggplot_lancet(aes(x = redcap_event_name, y = value, group = study_id)) + 
  geom_line(position=position_jitter(w=0.2, h=0.2), alpha = 0.2) + 
  facet_wrap(.~ name)
```


```{r}
# Set up EQ5D trajectories, probably joins easiest
## Set pre-COVID q1 to q5. 
phosp %>% 
  filter(is.na(redcap_repeat_instance)) %>% 
  filter(study_id == "3-12") %>% 
  # select(study_id, redcap_event_name, matches("eq5d5l_[q12345]*_pre_numeric")) %>% 
  select(study_id, redcap_event_name, matches("eq5d5l_[q1]*_pre_numeric")) %>% 
  group_by(study_id) %>% 
  #summarise(test = sum(eq5d5l_q1_pre_numeric, na.rm = TRUE))
  summarise(
    eq5d5l_q1_pre_numeric = case_when(
      !is.na(eq5d5l_q1_pre_numeric) & redcap_event_name == "3 Months (1st Research Visit)" ~ eq5d5l_q1_pre_numeric,
      !is.na(eq5d5l_q1_pre_numeric) & redcap_event_name == "Add. Planned Clinical Visits" ~ eq5d5l_q1_pre_numeric,
      !is.na(eq5d5l_q1_pre_numeric) & redcap_event_name == "6 Weeks" ~ eq5d5l_q1_pre_numeric,
      !is.na(eq5d5l_q1_pre_numeric) & redcap_event_name == "12 Months (2nd Research Visit" ~ eq5d5l_q1_pre_numeric,
      !is.na(eq5d5l_q1_pre_numeric) & redcap_event_name == "Unscheduled" ~ eq5d5l_q1_pre_numeric,
    )
  )
?first  
  
```



```{r}
# Set up EQ5D trajectories, probably joins easiest
## Set pre-COVID q1 to q5.
## Going to work with date instrument completed, so will not fill a missing question from another time point. 
## Therefore, work on assumption that if q1 non-missing, this is the event to use. 
phosp_eq5d_baseline = phosp %>% 
  filter(is.na(redcap_repeat_instance)) %>% 
  select(study_id, redcap_event_name, matches("eq5d5l_[q12345]*_pre_numeric")) %>% 

    # Arrange events in the order of priority for extracting pre-covid status
  mutate(
    redcap_event_name = fct_relevel(redcap_event_name,
                                   "3 Months (1st Research Visit)",
                                   "Add. Planned Clinical Visits",
                                   "6 Weeks",
                                   "12 Months (2nd Research Visit)",
                                   "Unscheduled")
  ) %>% 
  arrange(redcap_event_name) %>% 
  
  # Now take the first non-missing row
  drop_na(eq5d5l_q1_pre_numeric) %>% 
  group_by(study_id) %>% 
  slice(1) %>% 
  
  # Add in admission date which is what we will consider the baseline to be from
  left_join(phosp %>% select(study_id, crf1a_date_adm, crf1a_date_first_symptoms) %>% 
              # This fills missing admin date with symptom onset date, but doesn't do much at the moment
              # Left as coudl substitute another date. 
              mutate(crf1a_date_adm = coalesce(crf1a_date_adm, crf1a_date_first_symptoms)) %>% 
              drop_na()
  ) %>% 
  select(-crf1a_date_first_symptoms, -redcap_event_name) 
```


```{r fig.height=8, fig.width=12}
library(magrittr)
plot_data = phosp %>% 
  filter(is.na(redcap_repeat_instance)) %>% 
  select(study_id, redcap_event_name, eq5d_date, crf3a_visit_date, matches("eq5d5l_[q12345]*_numeric")) %>% 
  drop_na(eq5d5l_q1_numeric) %>% 
  # Dates first
  # eq5d_date better completed than crf3a_visit_date. Use this and fill with crf3avisit_date if missing
  mutate(
    eq5d_date = coalesce(eq5d_date, crf3a_visit_date)
  )  %>% 
  left_join(phosp_eq5d_baseline %>% select(study_id, crf1a_date_adm)) %>% 
  mutate(days_to_eq5d = (eq5d_date - crf1a_date_adm) %>% as.numeric()) %>% 
  select(-eq5d_date, -crf3a_visit_date, -crf1a_date_adm) %>% 
  pivot_longer(matches("eq5d5l_[q12345]*_numeric")) %>% 
  bind_rows(
    phosp_eq5d_baseline %>%
      rename_with(~ gsub("pre_", "", .x)) %>% 
      pivot_longer(matches("eq5d5l_[q12345]*_numeric")) %>% 
      mutate(redcap_event_name = "Baseline",
             days_to_eq5d = 0) %>% 
      select(-crf1a_date_adm)
  ) %>% 
  filter(days_to_eq5d >= 0) %>% 
  filter(days_to_eq5d < 500) %T>%
  {total_n <<- (.) %>% 
    distinct(study_id) %>% 
    dim() %>% 
    extract(1)} %>% 
  mutate(name = factor(name, 
                       levels = c("eq5d5l_q1_numeric", "eq5d5l_q2_numeric", "eq5d5l_q3_numeric",
                                  "eq5d5l_q4_numeric", "eq5d5l_q5_numeric"),
                       labels = c("Mobility", "Self-care", "Usual activities", "Pain/discomfort", "Anxiety/depression")
  )) %>% 
  
  # Bring baseline characteristics back in
  left_join(
    phosp %>% 
  
  # Fill through where necessary
  group_by(study_id) %>% 
  fill(crf3a_bmi_2levels, crf3a_bmi_5levels, .direction = "downup") %>% 
  ungroup() %>% 

  filter(redcap_event_name == "Hospital Discharge") %>% 
  filter(is.na(redcap_repeat_instance)) %>% 
  select(study_id, age_admission_factor, 
                crf1a_sex, 
                crf1b_eth_5levels, 
                imd_quintile,
                crf3a_bmi_2levels,
                crf3a_bmi_5levels, 
                no_comorbid_3levels)
  ) %>% 
  arrange(study_id, days_to_eq5d)  # Just to visualise
```


```{r fig.height=8, fig.width=12}
plot_data  %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value, group = study_id)) +
  geom_line(position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_wrap(. ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))
```

```{r fig.height=8, fig.width=12}
plot_data %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  geom_smooth() +
  facet_wrap(. ~ name) + 
  ggtitle("EQ5D following COVID-19",
          paste("n = ", total_n, "., Baseline function and time 0 is date of admission to hospital"))
```

```{r}
plot_data  %>% 
  drop_na(crf1a_sex) %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  # geom_smooth() +
  geom_line(aes(group = study_id), position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(crf1a_sex ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))

```

```{r}
plot_data  %>% 
  drop_na(crf1a_sex) %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value, colour = crf1a_sex)) +
  geom_smooth() +
  # geom_line(aes(group = study_id), position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(. ~ name) + 
  labs(x = "Days from hospital admission", colour = "") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))
```

```{r}
plot_data  %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  geom_smooth() +
  # geom_line(position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(age_admission_factor ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))

```

```{r}
plot_data  %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  geom_smooth() +
  # geom_line(position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(crf3a_bmi_2levels ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))

```

```{r}
plot_data  %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  # geom_smooth() +
  geom_line(aes(group = study_id), position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(crf1b_eth_5levels ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))

```




```{r}
plot_data2 = phosp %>% 
  filter(is.na(redcap_repeat_instance)) %>% 
  select(study_id, redcap_event_name, eq5d_date, crf3a_visit_date, matches("eq5d5l_[q12345]*_numeric")) %>% 
  drop_na(eq5d5l_q1_numeric) %>% 
  # Dates first
  # eq5d_date better completed than crf3a_visit_date. Use this and fill with crf3avisit_date if missing
  mutate(
    eq5d_date = coalesce(eq5d_date, crf3a_visit_date)
  )  %>% 
  left_join(phosp_eq5d_baseline %>% select(study_id, crf1a_date_adm)) %>% 
  mutate(days_to_eq5d = (eq5d_date - crf1a_date_adm) %>% as.numeric()) %>% 
  left_join(phosp_eq5d_baseline) %>% 
  mutate(
    eq5d5l_q1_numeric = eq5d5l_q1_numeric - eq5d5l_q1_pre_numeric,
    eq5d5l_q2_numeric = eq5d5l_q2_numeric - eq5d5l_q2_pre_numeric,
    eq5d5l_q3_numeric = eq5d5l_q3_numeric - eq5d5l_q3_pre_numeric,
    eq5d5l_q4_numeric = eq5d5l_q4_numeric - eq5d5l_q4_pre_numeric,
    eq5d5l_q5_numeric = eq5d5l_q5_numeric - eq5d5l_q5_pre_numeric,
  ) %>% 
  select(-eq5d_date, -crf3a_visit_date, -crf1a_date_adm,
         -matches("eq5d5l_[q12345]*_pre_numeric")) %>% 
  pivot_longer(matches("eq5d5l_[q12345]*_numeric")) %>% 
  bind_rows(
    phosp_eq5d_baseline %>%
      rename_with(~ gsub("pre_", "", .x)) %>% 
      pivot_longer(matches("eq5d5l_[q12345]*_numeric")) %>% 
      mutate(redcap_event_name = "Baseline",
             days_to_eq5d = 0,
             value = 0) %>% 
      select(-crf1a_date_adm)
  ) %>% 
  filter(days_to_eq5d >= 0) %>% 
  filter(days_to_eq5d < 500) %T>%
  {total_n <<- (.) %>% 
    distinct(study_id) %>% 
    dim() %>% 
    extract(1)} %>% 
  mutate(name = factor(name, 
                       levels = c("eq5d5l_q1_numeric", "eq5d5l_q2_numeric", "eq5d5l_q3_numeric",
                                  "eq5d5l_q4_numeric", "eq5d5l_q5_numeric"),
                       labels = c("Mobility", "Self-care", "Usual activities", "Pain/discomfort", "Anxiety/depression")
  )) %>% 
  
  # Bring baseline characteristics back in
  left_join(
    phosp %>% 
  
  # Fill through where necessary
  group_by(study_id) %>% 
  fill(crf3a_bmi_2levels, crf3a_bmi_5levels, .direction = "downup") %>% 
  ungroup() %>% 

  filter(redcap_event_name == "Hospital Discharge") %>% 
  filter(is.na(redcap_repeat_instance)) %>% 
  select(study_id, age_admission_factor, 
                crf1a_sex, 
                crf1b_eth_5levels, 
                imd_quintile,
                crf3a_bmi_2levels,
                crf3a_bmi_5levels, 
                no_comorbid_3levels)
  ) %>% 
  arrange(study_id, days_to_eq5d)  # Just to visualise
```












```{r}
plot_data2  %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value, group = study_id)) +
  geom_line(position=position_jitter(w=0.3, h=0.3), alpha = 0.1) + 
  facet_wrap(. ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))
```

```{r fig.height=8, fig.width=12}
plot_data2 %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  geom_smooth() +
  facet_wrap(. ~ name) + 
  ggtitle("EQ5D following COVID-19",
          paste("n = ", total_n, "., Baseline function and time 0 is date of admission to hospital"))
```

```{r}
plot_data2  %>% 
  drop_na(crf1a_sex) %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  # geom_smooth() +
  geom_line(aes(group = study_id), position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(crf1a_sex ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))

```

```{r}
plot_data2  %>% 
  drop_na(crf1a_sex) %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value, colour = crf1a_sex)) +
  geom_smooth(formula = y ~ s(x, bs = "ts")) +
  # geom_line(aes(group = study_id), position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(. ~ name) + 
  labs(x = "Days from hospital admission", colour = "") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))
```

```{r}
plot_data2  %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  geom_smooth() +
  # geom_line(position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(age_admission_factor ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))

```

```{r}
plot_data2  %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  geom_smooth() +
  # geom_line(position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(crf3a_bmi_2levels ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))

```

```{r}
plot_data2  %>% 
  ggplot_lancet(aes(x = days_to_eq5d, y = value)) +
  # geom_smooth() +
  geom_line(aes(group = study_id), position=position_jitter(w=0.3, h=0.3), alpha = 0.12) + 
  facet_grid(crf1b_eth_5levels ~ name) + 
  xlab("Days from hospital admission") +
  ggtitle("EQ5D following COVID-19",
          paste0("n = ", total_n, ". Baseline function and time 0 is date of admission to hospital"))

```

## Alluvial plot

```{r}
library(ggalluvial)
alluvial_data = phosp %>% 
  filter(is.na(redcap_repeat_instance)) %>% 
  select(study_id, redcap_event_name, matches("eq5d5l_[q12345]*_numeric")) %>% 
  drop_na(eq5d5l_q1_numeric) %>% 
  bind_rows(
    phosp_eq5d_baseline %>% 
  rename_with(~ gsub("pre_", "", .x)) %>% 
  mutate(redcap_event_name = "Baseline") %>% 
  select(-crf1a_date_adm)
  ) %>% 
  
  # Up to now then we have row per patient-event and each eq5d at those events
  ## Now make vertical factor for alluvial plot. 
  
  mutate(
    eq5d5l_status = select(., matches("eq5d5l_[q12345]*_numeric")) %>% 
      apply(1, function(.x){                                                                
        case_when(
          all(.x == 0) ~ "Perfect health",                                           
          any(.x == 1) ~ "Any 1",
          any(.x >= 2) ~ "Any 2+",
          all(is.na(.x)) ~ NA_character_,
          # TRUE ~  "Perfect health (missing 1+ domain)" # Very few here
          TRUE ~  "Perfect health"
        )
      }
      ) %>% 
      factor() %>% 
      fct_relevel("Perfect health", "Perfect health (missing 1+ domain)", "Any 1", "Any 2+")
  ) %>% 
  select(-matches("eq5d5l_[q12345]*_numeric")) %>% 
  pivot_wider(id_cols = study_id, names_from = redcap_event_name, values_from = eq5d5l_status) %>% 
  select(-study_id)
```

```{r}
alluvial_data %>% 
  count(`Baseline`, `6 Weeks`,  `3 Months (1st Research Visit)`, `12 Months (2nd Research Visit)`) %>% 
  ggforce::gather_set_data(., x = 1:(which(colnames(.)=="n")-1), id="alluvium") %>%
  dplyr::mutate(project = factor(x, levels = unique(x)),
                strata = factor(y, levels = unique(y))) %>% 
  # select only essential columns
  dplyr::select(project, strata, n, alluvium) %>%
  
  # plot data
  ggplot() +
  aes(x = project, y = n, alluvium = alluvium, stratum = strata, fill = strata, label = strata) +
  ggalluvial::geom_flow(stat = "alluvium", lode.guidance = "rightleft", aes.flow = "forward", colour = "black",
                        alpha = 0.6) +
  ggalluvial::geom_stratum(alpha = 0.6, colour = "black") +
  geom_text(stat = "stratum", size = 4, fontface = 2) +
  #scale_x_discrete("", labels = c("Admission location", "HDU/ITU after day 1", "Maximum treatment", "Outcome")) +
  scale_y_continuous(name = "Total Number of Patients") +
  scale_fill_brewer(palette = "Pastel1") +
  theme_classic(base_size = 18) + guides(fill=FALSE) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.line=element_blank())
```


```{r}
alluvial_data %>% 
  select(-`6 Weeks`) %>% 
  count(`Baseline`, `3 Months (1st Research Visit)`, `12 Months (2nd Research Visit)`) %>% 
  ggforce::gather_set_data(., x = 1:(which(colnames(.)=="n")-1), id="alluvium") %>%
  dplyr::mutate(project = factor(x, levels = unique(x)),
                strata = factor(y, levels = unique(y))) %>% 
  # select only essential columns
  dplyr::select(project, strata, n, alluvium) %>%
  
  # plot data
  ggplot() +
  aes(x = project, y = n, alluvium = alluvium, stratum = strata, fill = strata, label = strata) +
  ggalluvial::geom_flow(stat = "alluvium", lode.guidance = "rightleft", aes.flow = "forward", colour = "black",
                        alpha = 0.6) +
  ggalluvial::geom_stratum(alpha = 0.6, colour = "black") +
  geom_text(stat = "stratum", size = 4, fontface = 2) +
  scale_x_discrete("", labels = c("Baseline", "3 months", "12 months")) +
  scale_y_continuous(name = "Total Number of Patients") +
  scale_fill_brewer(palette = "Pastel1") +
  theme_classic(base_size = 18) + guides(fill=FALSE) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.line=element_blank())
```