---
title: "Hamish tables"
author: "PHOSP-COVID collaborative"
output:
  word_document:
    reference_docx: template.docx 
---

```{r setup, include=FALSE}
library(finalfit)
library(knitr)
library(tidyverse)
library(purrr)
library(rmarkdown)

summary_factorlist <- purrr::partial(finalfit::summary_factorlist, na_to_prop = FALSE)


mykable = function(x, row.names = FALSE){
    knitr::kable(x, row.names = row.names, align = c("l", "l", "r", "r", "r", "r", "r", "r", "r", "r", "r")) 
}

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r}
# Only run once for each new data pull
library(readr) # loaded with tidyverse anyway

# Use the phosp_clean dataset in safe haven

datadir = "/home/common/phosp/cleaned/full/"
timestamp = "2021-07-07_0400"
phosp   = read_rds(paste0(datadir, "phosp_", timestamp, "_full.rds")) # Use a version of phosp.rds here. 
```


Some of the labels that come from REDCap are long. Adjust these here. 

e.g.  Age at Admission (Years)Please enter date of birth (CRF0) and date of admission (CRF1A) to calculate.

```{r}
# Label changes
phosp = phosp %>% 
  mutate(
    age_admission = ff_label(age_admission, "Age (years)"),
    patient_sq_q_today = ff_label(patient_sq_q_today, "Occupation")
  )
```

Fix variables here

```{r}
# This replaces the variable on the left with the one on the right if missing.
## It looks a bit complicated, but is just an ifelse applied very efficiently

vars = c("patient_sq_l_b_seeing" = "patient_sq_l_b_seeing2",
         "patient_sq_l_b_hearing" = "patient_sq_l_b_hearing2",
         "patient_sq_l_b_walking" = "patient_sq_l_b_walking2",
         "patient_sq_l_b_remembering" = "patient_sq_l_b_remembering2",
         "patient_sq_l_b_self_care" = "patient_sq_l_b_self_care2",
         "patient_sq_l_b_communicate"= "patient_sq_l_b_communicate2",
         
         "psq_scale_blness_pre" = "psq_scale_blness_pre2",
         "psq_scale_cough_pre" = "psq_scale_cough_pre2",
         "psq_scale_fatigue_pre" = "psq_scale_fatigue_pre2",
         "psq_scale_sleep_pre" = "psq_scale_sleep_pre2",
         "psq_scale_pain_pre" = "psq_scale_pain_pre2"
)

expressions = imap(vars, ~ expr(if_else(is.na(!! sym(.y)), !! sym(.x), !! sym(.y))))

phosp = phosp %>%
  mutate(!!! expressions) %>% 
  ff_relabel_df(phosp)
```



## Table 1

Given that this is unpaired data, easiest just to make two separate tables and column-bind them. 

Will do this all from the main large phosp object.

```{r}
# I'm making phosp_hosp here, but if you have run the cleaning scripts above, this is not required
# You can start from here using the phosp_clean dataset. 

phosp_hosp = phosp %>% 
  filter(redcap_event_name == "Hospital Discharge") %>% # Select only baseline data
  filter(is.na(redcap_repeat_instance)) %>%  # Remove repeat instruments, bloods, PFTs etc. 
  filter(tier == 2) %>%                      # Tier 2 only
  purrr::discard(~all(is.na(.)))             # Remove empty columns

phosp_3m = phosp %>% 
  filter(redcap_event_name == "3 Months (1st Research Visit)") %>% # Select only 3 month data
  filter(is.na(redcap_repeat_instance)) %>%  # Remove repeat instruments, bloods, PFTs etc. 
  filter(tier == 2) %>%                      # Tier 2 only
  purrr::discard(~all(is.na(.)))             # Remove empty columns

phosp_12m = phosp %>% 
  filter(redcap_event_name == "12 Months (2nd Research Visit)") %>% # Select only 12 month data
  filter(is.na(redcap_repeat_instance)) %>%  # Remove repeat instruments, bloods, PFTs etc. 
  filter(tier == 2)  %>%                     # Tier 2 only
  purrr::discard(~all(is.na(.)))             # Remove empty columns
```

There are variables only available at baseline. Commonly used variables that don't change over time have been copied, through. 
Such as age and sex should appear in all instances, 3m, 12m etc. 

For these tables, they are mostly baseline variables with a smaller number of 3m and 12m. 

It is easier therefore to just join the relevant 3m / 12m variables back to phosp_hosp, which is baseline. I'll do that throughout.


```{r}
# Variables to present
explanatory = c("age_admission", 
             "age_admission_factor",
             "crf1a_sex", 
             "crf1b_eth_5levels", 
             
             # Occupation from 3m / 12m
             "patient_sq_q_today",
             
             # Healthcare worker from baseline
             "crf1b_healthcare_worker",
             
             "imd_quintile",
             "crf3a_bmi",
             "crf3a_bmi_2levels",
             "crf3a_bmi_5levels", 
             
             "patient_sq_n",
             
             # Comorbidities
             "no_comorbid",
             "no_comorbid_3levels",
             "crf1a_com_card", 
             "crf1a_com_mer",
             "crf1a_com_res",
             "crf1a_com_diab",
             
             "crf1a_com_rheu",
             "crf1a_com_gast", 
             "crf1a_com_neupsy",
             "crf1a_com_mh", 
             "crf1a_com_id",
             
             
             "crf1a_admission_duration",
             
             "crf1a_treat_ss", "crf1a_treat_at", "crf1a_treat_tdac")
```


```{r}
t1a = phosp_3m %>% 
  select(study_id, psq_recovered, patient_sq_q_today, patient_sq_n,
         crf3a_bmi, crf3a_bmi_2levels, crf3a_bmi_5levels, ) %>%  # take only what you need from 3m, including study_id
  left_join(phosp_hosp) %>% 
  summary_factorlist("psq_recovered", explanatory,
                     na_include = TRUE, na_include_dependent = TRUE,
                     total_col = TRUE,
                     add_col_totals = TRUE,
                     add_row_totals = TRUE, include_row_missing_col = FALSE, p = TRUE) %>% 
  relocate(           # Re-jig to join
    label = label,
    levels = levels,
    `Total N (3M)` = `Total N`)


t1b = phosp_12m %>% 
  select(study_id, psq_recovered, patient_sq_q_today, patient_sq_n,
         crf3a_bmi, crf3a_bmi_2levels, crf3a_bmi_5levels, ) %>%  # take only what you need from 3m, including study_id
  left_join(phosp_hosp) %>% 
  summary_factorlist("psq_recovered", explanatory,
                     na_include = TRUE, na_include_dependent = TRUE,
                     total_col = TRUE,
                     add_col_totals = TRUE,
                     add_row_totals = TRUE, include_row_missing_col = FALSE, p = TRUE) %>% 
    relocate(           # Re-jig to join
    label = label,
    levels = levels,
    `Total N (12M)` = `Total N`)
```

```{r}
bind_cols(t1a, 
          t1b[,3:9],
          .name_repair = c("minimal")) %>% 
  mykable() # Danger danger, not labelling 12 months specifically. 
```






## Table 2

This is more difficult because the variables come from different.

Again, do these in 3 separate steps. The pre data will just come from 3 months for now. 


```{r}
explanatory_pre = c("eq5d5l_summary_pre",
                    "eq5d5l_q1_pre",
                    "eq5d5l_q2_pre",
                    "eq5d5l_q3_pre",
                    "eq5d5l_q4_pre",
                    "eq5d5l_q5_pre",
                    
                    "patient_sq_l_b_seeing",
                    "patient_sq_l_b_hearing",
                    "patient_sq_l_b_walking",
                    "patient_sq_l_b_remembering",
                    "patient_sq_l_b_self_care",
                    "patient_sq_l_b_communicate",
                    
                    "psq_scale_blness_pre",
                    "psq_scale_cough_pre",
                    "psq_scale_fatigue_pre",
                    "psq_scale_sleep_pre",
                    "psq_scale_pain_pre"
                    
)

explanatory_current = c("eq5d5l_summary",
                        "eq5d5l_q1",
                        "eq5d5l_q2",
                        "eq5d5l_q3",
                        "eq5d5l_q4",
                        "eq5d5l_q5",
                        
                        "patient_sq_l_t_seeing",
                        "patient_sq_l_t_hearing",
                        "patient_sq_l_t_walking",
                        "patient_sq_l_t_remembering",
                        "patient_sq_l_t_self_care",
                        "patient_sq_l_t_communicate",
                        
                        "psq_scale_blness_since",
                        "psq_scale_cough_since",
                        "psq_scale_fatigue_since",
                        "psq_scale_sleep_since",
                        "psq_scale_pain_since"
)


t2_pre = phosp_3m %>%
  summary_factorlist(dependent = NULL,  explanatory_pre,
                     na_include = TRUE, na_include_dependent = TRUE,
                     add_col_totals = TRUE,
                     add_row_totals = TRUE, include_row_missing_col = FALSE) %>% 
  relocate(
    label = label,
    levels = levels,
    `Total N (pre)` = `Total N`,
     "Pre-hospitalisation" = "all")

t2_3m = phosp_3m %>%
  summary_factorlist(dependent = NULL,  explanatory_current,
                     na_include = TRUE, na_include_dependent = TRUE,
                     add_col_totals = TRUE,
                     add_row_totals = TRUE, include_row_missing_col = FALSE) %>% 
    relocate(
    label = label,
    levels = levels,
    `Total N (3M)` = `Total N`,
     "3 month" = "all")
  

t2_12m = phosp_12m %>%
  summary_factorlist(dependent = NULL,  explanatory_current,
                     na_include = TRUE, na_include_dependent = TRUE,
                     add_col_totals = TRUE,
                     add_row_totals = TRUE, include_row_missing_col = FALSE) %>% 
    relocate(
    label = label,
    levels = levels,
    `Total N (12 month)` = `Total N`,
     "12 month" = "all")
```

```{r}
bind_cols(t2_pre,
          t2_3m[, c(3,4)],
          t2_12m[, c(3,4)]) %>% 
  mykable()
```





